### 2015-06-15 writing/S'15 LSTM/discussion.tex
Paper push.
Learning curve

@@

The results are shown in Figure~\ref{prop-results}\todo{Next version of figures will have vertical dividing lines at 3,4,6}. All four models were able to largely memorize the training data (TODO, TODO, TODO, and TODO for $\le$6, pooling across bins). In the $\le$6 setting, the three tree models were able to perform at above TODO\% on examples of size $\le$2 with a steady decay in performance continuing through TODO\% at size 12, and similar, if steeper, decays with smaller training sets. All four robustly beat the simple baselines reported in Bowman et al.: the most frequent class occurs just over 50\% of the time, and a summing model that ignores word order does reasonably on the shortest examples but falls below 60\% by bin 4.

The LSTM performs fairly poorly in the $\le3$ setting, with performance at 3 a mediocre TODO\%, and an abrupt drop to TODO\% at 4, suggesting that the model did not acquire the needed generalizations. With more ample training data in the $\le6$ condition, though, the LSTM shows fairly good accuracy on short examples, and a smooth decay with no abrupt drop.

Learning curve experiments suggest that none of these models are saturated, and that still larger data sets could help even on this simple task. The LSTM in the $\le6$ strikingly moves from TODO\% accuracy with a random 33\% of the available training data to TODO\% on all of it. The plain TreeRNN shows the smallest improvement, moving from TODO\% to TODO\%.

>>>>

\begin{figure}[t]
  \centering
      \includegraphics[height=1.1in]{lcc.pdf}
  \caption{Learning curve for the $\le6$ experiment.}
  \label{fig:lc} 
\end{figure}

@@

The results are shown in Figure~\ref{prop-results}. All four models were able to largely memorize the training data (??.?, ??.?, ??.?, and ??.? for $\le$6, pooling across bins). In the $\le$6 setting, the three tree models were able to perform at above ??\% on examples of size $\le$2 with a steady decay in performance continuing through ??.?\% at size 12, and similar, if steeper, decays with smaller training sets. All four robustly beat the simple baselines reported in Bowman et al.: the most frequent class occurs just over 50\% of the time, and a summing model that ignores word order does reasonably on the shortest examples but falls below 60\% by bin 4.

The LSTM performs fairly poorly in the $\le3$ setting, with performance at 3 a mediocre ??.?\%, and an abrupt drop to \% at 4, suggesting that the model did not acquire the needed generalizations. With more ample training data in the $\le6$ condition, though, the LSTM shows fairly good accuracy on short examples, and a smooth decay with no abrupt drop.

The learning curve (Figure~\ref{fig:lc}) suggests that additional data is unlikely to change these basic results, though the disparity in performance at the 11\% level is striking: the LSTM sequence model and the TreeRNTN (the model with the most parameters by far) lag far behind the other two.
